### 2024-08-17 paper.tex
m

\section{Finding the irreducible components of \(U_0\)}
Let \(X\) be nilpotent with Jordan basis \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\).
Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
Let
\[U_0 = \{(A_{0,b}, U) \in V\}.\]
We will find the irreducible components of \(U_0\).

@@

\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
For each row \(i\), let \(p_i = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
Then set \(q_i = \lambda_i - p_i\).
Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).

>>>>

\section{Finding the irreducible components of \(U_0\)}
Let \(X\) be nilpotent with Jordan basis \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\).
Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
Let
\[U_0 = \{(A_{0,b}, U) \in V\}.\]
We will find the irreducible components of \(U_0\).
\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
Then set \(q_i(b) = \lambda_i - p_i(b)\).
When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).

For any \(I' \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I'}\) such that (1) \(\rho_i \leq \lambda_i\) and (2) \(\rho_i\) is decreasing with \(i\), define 
\[U_{I', (\rho_i)} := \{(A_{0, b}, U) \in U_0 : I' = \{i : p_i > \max_{j : q_j > q_i} p_j\} \land \forall i \in I'. \; p_i = \rho_i \}.\]
\begin{lemma}
    \(U_0 = \bigcup_{I', (\rho_i)} U_{I', (\rho_i)}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that \(\rho_i\) is decreasing as \(i\) increases.
\end{lemma}
\begin{proof}
    Let \((A_{0, b}, U) \in U_0\).
    Define \(I' = \{i : p_i > \max_{j : q_j > q_i} p_j\}\), and for \(i \in I'\), \(\rho_i := p_i\).
    All we need to do is show that each \(\rho_i\) is positive and that \(\rho_i\) is decreasing.
    Then we get that \((A_{0,b}, U) \in U_{I', (\rho_i)}\), and we are done.
    \par Recall that by convention we take that the maximum of the empty set is zero.
    So, the fact that \(\rho_i > \max_{j : q_j > q_i} p_j\) tells us that \(\rho_i\) is positive.
    Now, let \(i < i'\), with \(i, i' \in I'\).
    If we had \(p_i \leq p_{i'}\), then \(q_i \geq q_{i'}\)

@@

\par Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
